### 2020-05-18 paper/main.tex
ALG III

\section{Notes}
\begin{itemize}
	\item $V(X)$ -- vertices of structure $X$. Will be written as $X$ when obvious.
	\item $a - b$, when $a$ and $b$ are nodes -- $a$ and $b$ are neighbors.
	\item $a - X$, when $a$ is a node and $X$ is a set of nodes -- $a$ is complete to $X$.
	\item $a \cdots b$, when $a$ and $b$ are nodes -- $a$ and $b$ are not neighbors.
	\item $a \cdots X$, when $a$ is a node and $X$ is a set of nodes -- $a$ is anticomplete to $X$.
	\item $[n]$  -- $\{1, \ldots, n\}$.
	\item \LGBSK -- a line-graph of a biparite subdivision of $K_4$.
\end{itemize}

@@

>>>>

\section{Notes}
\begin{itemize}
	\item $V(X)$ -- vertices of structure $X$. Will be written as $X$ when obvious.
	\item $a - b$, when $a$ and $b$ are nodes -- $a$ and $b$ are neighbors.
	\item $a \cdots b$, when $a$ and $b$ are nodes -- $a$ and $b$ are not neighbors.
	\item $a - X$, when $a$ is a node and $X$ is a set of nodes -- $a$ has a neighbor in $X$.
	\item $a \cdots X$, when $a$ is a node and $X$ is a set of nodes -- $a$ has a nonneighbor in $X$.
	\item $a \blacktriangleleft  X$, when $a$ is a node and $X$ is a set of nodes -- $a$ is complete to $X$.
	\item $a \ntriangleleft X$, when $a$ is a node and $X$ is a set of nodes -- $a$ is anticomplete to $X$.
	\item $X \setComplete Y$, when $X$ and $Y$ are set of nodes -- $X$ is complete to $Y$.
	\item $X \setAntiComplete Y$, when $X$ and $Y$ are set of nodes -- $X$ is anticomplete to $Y$.
	\item $[n]$  -- $\{1, \ldots, n\}$.
	\item \LGBSK -- a line-graph of a biparite subdivision of $K_4$.
	\item $a \gets b$ -- let a be equal b.
	\item $a :\in X$ -- let a be equal to any element of $X$
	\item $a \xor b$ -- $a$ xor $b$
\end{itemize}

@@

\input{algIII.tex}
